Network Cascades

### 2016-08-25 paper/paper.tex
Give them another one for motivation

% TODO: At least one more example

>>>>

To give another example, the model of network cascades can help to explain how some cultural artifacts like books or movies can emerge out of obscurity, while other artifacts never receive the attention of the general public, although being qualitatively comparable on an objective level. The basic assumption here is that the audience will make the decision of wether to give an artifact (a product) attention based on their observation of their social neighbors, rather than on their personal information. ``If all other people in my group of friends are reading a book then I too should read that book''.

Research in this area is in particular interest for marketing, where understanding the dynamics of the target marked network can lead to important insights on how to promote a product and hopefully encourage a cascade in said network, resulting in favorable sales figures.
